GRASS image processing environment\\ Gearing towards GRASS 7

### 2013-03-13 grassposter/2013_EGU_G7/poster.tex
pdf qr codes instead of png
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55349 15284696-431f-4ddb-bdfa-cd5b030d7da7
Modified the status of temporal GIS to -finished-
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55351 15284696-431f-4ddb-bdfa-cd5b030d7da7
2013_EGU_G7: use vector logos
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55352 15284696-431f-4ddb-bdfa-cd5b030d7da7

\addlogo[north west]{(2,-1)}{9cm}{./images/Grass_GIS.png}
\addlogo[north east]{(-2,-2.5)}{11cm}{./images/iwmi.png}

\blocknode{Abstract}{
\small GRASS 7 started its development by the branching out of GRASS 6.x from the main trunk of code (rev 31142).
This was done on 27th of April 2008, and a large amount of changes took place since that date, more 
are still underway.
\begin{itemize}
 \item Display library in GRASS 7 (planning \& ongoing)
 \item Raster library in GRASS 7 (planning \& ongoing)
 \item Vector library in GRASS 7 (planning \& ongoing)
 \item G3d (volume) library and modules in GRASS 7 (finished)
 \item Temporal extension for GRASS 7 (planning state) 
\end{itemize}

@@

\begin{center}
\begin{tabular}{cp{0.9\textwidth}}
\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/iwmiqr.png}
\end{minipage}

@@

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/Grass_qr.png}
\end{minipage}

>>>>

\addlogo[north west]{(2,-1)}{9cm}{./images/Grass_GIS.pdf}
\addlogo[north east]{(-2,-2.5)}{11cm}{./images/IWMI_logo.pdf}

\blocknode{Abstract}{
\small GRASS 7 started its development by the branching out of GRASS 6.x from the main trunk of code (rev 31142).
This was done on 27th of April 2008, and a large amount of changes took place since that date, more 
are still underway.
\begin{itemize}
 \item Display library in GRASS 7 (planning \& ongoing)
 \item Raster library in GRASS 7 (planning \& ongoing)
 \item Vector library in GRASS 7 (planning \& ongoing)
 \item G3d (volume) library and modules in GRASS 7 (finished)
 \item Temporal extension for GRASS 7 (finished) 
\end{itemize}

@@

\begin{center}
\begin{tabular}{cp{0.9\textwidth}}
\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/iwmi_qr.pdf}
\end{minipage}

@@

\begin{minipage}{0.15\textwidth}
\includegraphics[width=0.7in]{./images/grass_qr.pdf}
\end{minipage}
